\chapter*{Acknowledgement}
\thispagestyle{plain}
I would like to express my special thanks of gratitude to my supervisor and teacher Dr. Attila Magyar as well as our principal of the doctoral school Prof. Katalin Hangos who gave me the wonderful opportunity to pursue this excellent project on optimal current control, which also helped me to develop and better myself on the field of scientific work, where I could really see myself grow and develop. I really feel gratitude to them. I would like to also thank Dr. Nimród Kutasi, and his restless support and encouragement in the filed of predictive control, as well as Dr. András Kelemen in the field of power electronics. Without they unquestionable and deep technical knowledge on the field, and they helpfulness, kindness and hospitality this doctoral thesis would not have happened. I would also recognise Dr. Peter Görbe who helped me to put the subject of voltage quality in context and accelerated my progress at the start of my PhD. studies, and Dr. Attila Fodor, who helped me on the filed of current control, and system modeling, and also helped me organise my work and guide me in the forest of research. All of they contribution were invaluable to reach this stage of completion.\\
Any attempt at any level can't be satisfactorily completed without the support and guidance of my spouse Klaudia, my parents Anikó and László, my sister Elisabeth, and my friends. They helped me a lot with they spiritual and financial support in making this project, despite of their busy schedules. They always could find enough time and energy to give me enough attention and assistance.\\
I could not thank you enough!

\newpage
\null
\thispagestyle{empty}%
\newpage


