
    Recently, due to the growth of distributed generation from renewable energy sources the nature of the electrical power grid tends to alter from a passive network to an active one.
    In this new environment, the importance and difficulty of maintaining the security and operational stability of the distribution system are increasing together. As opposed to
    this expectation most of the household renewable sources and loads are unevenly distributed single phase power converters, some of them representing high power consumption. Ideal generators supply symmetrical three-phase sinusoidal positive sequence voltages, which are balanced
    in terms of their amplitudes phase differences at a single frequency. The terminology of unbalance can be divided into amplitude unbalance, phase difference unbalance, and
    unbalanced harmonic disturbance. The occurrence of at least one of these features is enough for a distribution network to become unbalanced. The situation is further exacerbated
    by the stochastic on/off switching of the different types of loads which causes stochastic disturbing unbalance in the load currents which cases unbalanced load of the low voltage
    transformer, and causes amplitude and phase unbalance in the voltage phasor trough the serial impedance of the low voltage transportation line wires and connecting devices cables.
    Many countries have changed their regulating laws about power supply to allow for grid-tie inverter systems to provide spare power from renewable sources to local low voltage
    grids. The unbalance of the grid is further increased by using single phase grid tie inverter systems in the size of typical small household power plants (1 - 50\,kW) and the
    produced electrical power originating from renewable power source (wind and solar) also admits stochastic behavior. This unbalance yields to a suboptimal operation of low voltage three phase transformers to generate undesirable additional power loss and increase in the probability of malfunction of the low voltage energy transportation system. The effective current unbalance causes additional power loss of the transportation line resistances too.

    Single phase power injections to the grid are mainly generated by domestic photovoltaic-(PV) and wind power plants. Many current references about the renewable energy sources
    integration to the low voltage grid ad short time and long time storage ready for connection of this electrical energy in the literature can be found. For off-grid solutions sometimes more complex solutions integrating diesel generators, PV and wind generators are proposed, e.g. in \cite{shezan2016}.
    \cite{cucchiella2013environmental} were presented the economical aspects of a PV system. The economic results are strongly influenced by the annual average insolation value,
    which encourages the areas most exposed to the sun and the southern areas. The consumption of consumers is not critically important, but the design principle used has as
    significant effect on the maximization of the performance of PV plants. \cite{kaldellis2009optimum} notify, that autonomous photovoltaic systems are strongly
    responsible of their reactive energy requirements. To support photovoltaic systems with battery banks sustainable character one should be able to establish that their reactive energy
    requirement share fairly compensated by the corresponding energy yield.  Additionally, \cite{ortega2013measurement} emphasize that PV systems are increasingly
    being deployed in all over the world, and this is the source of a wide range of power quality problems. With a view to consistently measuring and assessing the power quality characteristics of PV
    systems, they had presented an in-depth overview and discussion of this topic. The study by \cite{huat2015integration} explored integration issues of electric vehicle battery packs. They suggest that high voltage battery packs with large format cells has advantages in assembly, thermal management, monitoring and control, services and maintenance. On the other hand, quality, reliability and limited specific energy of large format cells are obstacles need to overcome. Solving these problems will further affect the cost, performance, reliability and safety of the electric vehicles. Smart energy systems in specially in urban areas are discussed in \cite{lund2015smart} where a design methodology has been suggested.

    There are different consequences of unbalance. \cite{lee1998effects} were discussing the effects of unbalanced voltage on a three-phase induction motor, one has to consider not only negative-sequence voltage but also the positive-sequence voltage. With the same voltage unbalance factor, the status of voltage unbalance could be judged by the magnitude of positive sequence voltage. Also the effect of voltage unbalance has been studied on three-phase four-wire distribution networks for different control strategies for three-phase inverter-connected distributed generation units on voltage unbalance in distribution networks (\cite{meersman2011three}). Here the negative-sequence component and the zero sequence component were studied where unbalance conditions could lower stability margin and increasing the power losses. On the other hand, the adaptive coordination of distribution systems included distributed generation is also an emerging problem as it was discussed by \cite{ates2016}.  A small voltage unbalance might lead to a significant current unbalance because of low negative sequence impedance (\cite{bina2011three}) too. There are different approaches of lowering the unbalance with different control techniques. Additionally, new computationally efficient control techniques have been presented by \cite{lee2009new} to estimate and compensate input voltage-unbalance disturbances for a voltage source converter. These tools are designed to be effective with high power systems with slower PWM switching frequencies of 5 kHz or lower and limited current-controller bandwidth. About the unbalance compensation control aspect, a three-phase IGBT-based static synchronous compensator were proposed for voltage and/or current unbalance compensation by \cite{xu2010voltage}. An instantaneous power theory was used for real-time calculation and control. Three control schemes current control, voltage control and integrated control were proposed to compensate unbalanced voltage, unbalanced current or both.The unbalance phenomena and power quality can be examined with modeling too. A particular modeling method was presented by \cite{li2005microgrid} where a three-phase four-wire grid-interfacing power quality compensator were modeled. During grid voltage unbalance, the compensator, used a shunt and a series four phase inverter, and could enhance both the quality of power within the microgrid and the quality of currents flowing between the microgrid and utility system. The shunt four-leg inverter were controlled to maintain a set of balanced distortion free voltages to regulate power sharing among the parallel-connected distributed generation systems. Simulation studies were carried out by \cite{Hu2016264} where one of the aims was to develop and test the feasibility of a decoupled three-phase on-load tap charger in the distribution system with the objective of improving the distribution network power quality. Further control methods were applied for the solution for balancing of the most sensitive with regard to electric energy quality part of power system by \cite{uimethod},  minimizing the active power losses, stabilization of three-phase voltages, enhancement of asynchronous machine performance stability and reduction of errors occurring in power consumption measuring circuits. Further control methods were applied for the solution for balancing of the most sensitive with regard to electric energy quality part of power system in \cite{uimethod},  minimizing the active power losses, stabilization of three-phase voltages, enhancement of asynchronous machine performance stability and reduction of errors occurring in power consumption measuring circuits.In our Department we have antecedents of research of power quality in low voltage  distribution grid. A previous work of \cite{gorbe2012reduction} a complex control unit has been proposed that is capable of lowering extant harmonic distortion. In the work of \cite{Gorbe2014experimental} the effect of a small domestic (photovoltaic) power plant on the power quality, mainly the total harmonic distortion has been examined. The aim of this work is to \textcolor{magenta}{examine and compensate three phase voltage asymmetry of the electrial network based on the extended simulation model proposed by \cite{gorbe2012reduction}}.

    In many articles the authors presents a different viewpoint of calculating unbalance on the network. \cite{martin2015unbalance} showed to assess the harmonic distortion and the unbalance introduced by the different loads connected to the same point of common coupling have been applied to an experimental distribution network.  By \cite{kini2007novel} the focus was to bring out the ambiguity that crops up when we refer to a particular value of voltage unbalance that exists in the system. By making use of the complex nature of voltage unbalance, the voltage combinations that lead to the calculation of complex voltage unbalance factor could be narrowed down to a great extent. A fast and accurate algorithm for calculating unbalance has been presented by \cite{wen2014approximate}. The magnitudes of zero, positive, and negative sequences are obtained through simple algebraic equations based on the geometric figure, which is also called as 4 and 8 geometric partitions. Also a three-phase optimal power flow calculation methodology has been presented by \cite{araujo2013three}, that is suitable for unbalanced power systems. The optimal algorithm uses the primal-dual interior point method as an optimization tool in association with the three-phase current injection method in rectangular coordinates.%

    $$ ============================== $$

    Current source rectifiers (CSR) are widely used in frond-end power electronic converter for the uncontrollable or controllable DC-bus in industrial and commercial applications. They have maintained their position through many applications, with uses such as medium-voltage high-power drives \cite{vajda2017limiting}, \cite{ghalem2010six} STATCOMs \cite{gupta2014two} and renewable systems \cite{chen2016single}, \cite{exposto2015predictive}. They have a plain and reliable circuit structure, which makes them attractive for simple control design. The CSRs are traditionally controlled by classic cascaded linear control loops such as PI controllers. These simple control applications are suitable for induction motor control \cite{chebre2011speed}, and other electromechanical actuators \cite{salloum2014robust}, and unusual topologies \cite{neukirchner2017voltage}. Also, worth mentioning of self-tuning variants of PI controllers \cite{tahri2012digital}. In the past, the modulation methods used were trapezoidal pulse width modulation techniques (TPWM), or application of pulse patterns calculated offline for selective harmonic elimination (SHE). More recently, current space vector modulation (SVM) has been used for the synthesis of the transistor control signals \cite{gao2017model}. Even so, AC-side harmonic elimination could still be an issue at lower switching frequencies where LCL filtering would be advised \cite{han2010control}. In order to keep switching frequencies low and to minimize switching losses, new topologies and hybrid modulations are used, mixing TPWM and SHE depending on the grid frequency \cite{venkatraman2018multilevel}.
    In terms of the amplitude of the grid and DC-link voltages, CSRs exhibit a step-down conversion. When used as DC voltage source, the rectifier can output a lower DC voltage without the need of a grid-side transformer, as is usually employed in voltage source rectifiers (VSR). Because of their current source behaviour, CSRs can be easily paralleled and provide inherent short-circuit protection, representing an excellent potential in DC power supply applications \cite{feroura2017finite}, \cite{yan2015study}.
    There are several control strategies in addition to classical PI control for applications in this domain. Self-adapting control methods are on the rise with more sophisticated algorithms in the field of fuzzy logic \cite{urmos2017application}. They are capable of handling increasingly more complicated models and systems with high dynamics and accuracy \cite{chatterjee2008augmented}, \cite{haidegger2012simulation}, and even without establishing and validating classical state-space models \cite{vrkalovic2018model}. The other filed is the sliding mode control, which can achieve good dynamic performance and handle non-linearity. Still, they might also introduce chattering, which can be very undesirable when applied to real-life systems like in \cite{regaya2014new} and \cite{szell2014mathematical}.
    In the linear domain implicit model predictive control (IMPC or just MPC) is a fair solution due its effectiveness in power electronics due to its configurable cost function and such scalable nature \cite{kelemen2010constrained}, \cite{ahmed2014model}. In this field also finite-state solutions are present which can be considered also predictive control, where the modulation scheme’s defined states serve as optimization potential \cite{rivera2013predictive}, \cite{godlewska2015predictive}. As a further step adaptive application was established to tackle parameter estimation problems for better performance \cite{muthukumar2016adaptive}
    Recently, beside implicit, finite-state, and adaptive predictive control, explicit model predictive control has emerged in the field of power electronics \cite{kutasi2010constrained}. Establishing the MPC cost function can range widely depending on the expected dynamics, degree of noise cancellation, and model complexity. Additionally, the current limitation can also be implemented introducing constraints in the modulation algorithm.
    In \cite{ahmed2014model} the validity of an MPC-based, digital pulse width modulation control strategy for single-phase voltage source rectifiers is discussed, further confirming the validity of this method in control systems.


    %$$ ============================== $$

    %% no \IEEEPARstart
%    %\textcolor{magenta}{ATTILA, PETI}\\
%    Recently, due to the growth of distributed generation from renewable energy sources the nature of the electrical power grid tends to alter from a passive network to an active one.
%    In this new environment, the importance and difficulty of maintaining the security and operational stability of the distribution system are increasing together. As opposed to
%    this expectation most of the household renewable sources and loads are unevenly distributed single phase power converters, some of them representing high power consumption. Ideal generators supply symmetrical three-phase sinusoidal positive sequence voltages, which are balanced
%    in terms of their amplitudes phase differences at a single frequency. The terminology of unbalance can be divided into amplitude unbalance, phase difference unbalance, and
%    unbalanced harmonic disturbance. The occurrence of at least one of these features is enough for a distribution network to become unbalanced. The situation is further exacerbated
%    by the stochastic on/off switching of the different types of loads which causes stochastic disturbing unbalance in the load currents which cases unbalanced load of the low voltage
%    transformer, and causes amplitude and phase unbalance in the voltage phasor trough the serial impedance of the low voltage transportation line wires and connecting devices cables.
%    Many countries have changed their regulating laws about power supply to allow for grid-tie inverter systems to provide spare power from renewable sources to local low voltage
%    grids. The unbalance of the grid is further increased by using single phase grid tie inverter systems in the size of typical small household power plants (1 - 50\,kW) and the
%    produced electrical power originating from renewable power source (wind and solar) also admits stochastic behavior. This unbalance yields to a suboptimal operation of low voltage three phase transformers to generate undesirable additional power loss and increase in the probability of malfunction of the low voltage energy transportation system. The effective current unbalance causes additional power loss of the transportation line resistances too.
%
%    Single phase power injections to the grid are mainly generated by domestic photovoltaic-(PV) and wind power plants. Many current references about the renewable energy sources
%    integration to the low voltage grid ad short time and long time storage ready for connection of this electrical energy in the literature can be found. \textcolor{red}{For off-grid solutions sometimes more complex solutions integrating diesel generators, PV and wind generators are proposed, e.g. in \cite{shezan2016}.}
%    \cite{cucchiella2013environmental} were presented the economical aspects of a PV system. The economic results are strongly influenced by the annual average insolation value,
%    which encourages the areas most exposed to the sun and the southern areas. The consumption of consumers is not critically important, but the design principle used has as
%    significant effect on the maximization of the performance of PV plants. \cite{kaldellis2009optimum} notify, that autonomous photovoltaic systems are strongly
%    responsible of their reactive energy requirements. To support photovoltaic systems with battery banks sustainable character one should be able to establish that their reactive energy
%    requirement share fairly compensated by the corresponding energy yield.  Additionally, \cite{ortega2013measurement} emphasize that PV systems are increasingly
%    being deployed in all over the world, and this is the source of a wide range of power quality problems. With a view to consistently measuring and assessing the power quality characteristics of PV
%    systems, they had presented an in-depth overview and discussion of this topic. The study by \cite{huat2015integration} explored integration issues of electric vehicle battery packs. They suggest that high voltage battery packs with large format cells has advantages in assembly, thermal management, monitoring and control, services and maintenance. On the other hand, quality, reliability and limited specific energy of large format cells are obstacles need to overcome. Solving these problems will further affect the cost, performance, reliability and safety of the electric vehicles. \textcolor{red}{Smart energy systems in specially in urban areas are discussed in \cite{Lund2015} where a design methodology has been suggested.}
%
%    There are different consequences of unbalance. \cite{lee1998effects} were discussing the effects of unbalanced voltage on a three-phase induction motor, one has to consider not only negative-sequence voltage but also the positive-sequence voltage. With the same voltage unbalance factor, the status of voltage unbalance could be judged by the magnitude of positive sequence voltage. Also the effect of voltage unbalance has been studied on three-phase four-wire distribution networks for different control strategies for three-phase inverter-connected distributed generation units on voltage unbalance in distribution networks (\cite{meersman2011three}). Here the negative-sequence component and the zero sequence component were studied where unbalance conditions could lower stability margin and increasing the power losses. \textcolor{red}{On the other hand, the adaptive coordination of distribution systems included distributed generation is also an emerging problem as it was discussed by \cite{ates2016}.}  A small voltage unbalance might lead to a significant current unbalance because of low negative sequence impedance (\cite{bina2011three}) too. There are different approaches of lowering the unbalance with different control techniques. Additionally, new computationally efficient control techniques have been presented by \cite{} to estimate and compensate input voltage-unbalance disturbances for a voltage source converter. These tools are designed to be effective with high power systems with slower PWM switching frequencies of 5 kHz or lower and limited current-controller bandwidth. About the unbalance compensation control aspect, a three-phase IGBT-based static synchronous compensator were proposed for voltage and/or current unbalance compensation by \cite{xu2010voltage}. An instantaneous power theory was used for real-time calculation and control. Three control schemes current control, voltage control and integrated control were proposed to compensate unbalanced voltage, unbalanced current or both.The unbalance phenomena and power quality can be examined with modeling too. A particular modeling method was presented by \cite{li2005microgrid} where a three-phase four-wire grid-interfacing power quality compensator were modeled. During grid voltage unbalance, the compensator, used a shunt and a series four phase inverter, and could enhance both the quality of power within the microgrid and the quality of currents flowing between the microgrid and utility system. The shunt four-leg inverter were controlled to maintain a set of balanced distortion free voltages to regulate power sharing among the parallel-connected distributed generation systems. Simulation studies were carried out by \cite{Hu2016264} where one of the aims was to develop and test the feasibility of a decoupled three-phase on-load tap charger in the distribution system with the objective of improving the distribution network power quality. Further control methods were applied for the solution for balancing of the most sensitive with regard to electric energy quality part of power system by \cite{uimethod},  minimizing the active power losses, stabilization of three-phase voltages, enhancement of asynchronous machine performance stability and reduction of errors occurring in power consumption measuring circuits. Further control methods were applied for the solution for balancing of the most sensitive with regard to electric energy quality part of power system in \cite{uimethod},  minimizing the active power losses, stabilization of three-phase voltages, enhancement of asynchronous machine performance stability and reduction of errors occurring in power consumption measuring circuits. In our Department we have antecedents of research of power quality in low voltage distribution grid. A previous work of \cite{gorbe2012reduction} a complex control unit has been proposed that is capable of lowering extant harmonic distortion \textcolor{magenta}{in simulation environment}. In the work of \cite{Gorbe2014experimental} the effect of a small domestic (photovoltaic) power plant on the power quality, mainly the total harmonic distortion has been examined. The aim of this work is to extend the simulation model proposed by \cite{gorbe2012reduction} and examine \textcolor{magenta}{, and later compensate} three phase voltage asymmetry of the \textcolor{magenta}{modeled} network.
%
%    In many articles the authors presents a different viewpoint of calculating unbalance on the network. \cite{martin2015unbalance} showed to assess the harmonic distortion and the unbalance introduced by the different loads connected to the same point of common coupling have been applied to an experimental distribution network.  By \cite{kini2007novel} the focus was to bring out the ambiguity that crops up when we refer to a particular value of voltage unbalance that exists in the system. By making use of the complex nature of voltage unbalance, the voltage combinations that lead to the calculation of complex voltage unbalance factor could be narrowed down to a great extent. A fast and accurate algorithm for calculating unbalance has been presented by \cite{wen2014approximate}. The magnitudes of zero, positive, and negative sequences are obtained through simple algebraic equations based on the geometric figure, which is also called as 4 and 8 geometric partitions. Also a three-phase optimal power flow calculation methodology has been presented by \cite{araujo2013three}, that is suitable for unbalanced power systems. The optimal algorithm uses the primal-dual interior point method as an optimization tool in association with the three-phase current injection method in rectangular coordinates.% 